### 2022-07-14 main.tex
de-confuse self

We therefore extend our model to consider the effects of generalized \textit{non-symptomatic} transmission, which includes both pre-symptomatic and asymptomatic transmission (Supplementary Figure S1), to ask the following question:
does an intermediate amount of non-symptomatic transmission lead to a peak in fatalities?
For this model, we assume that $\delta$ decreases transmission only after symptom onset.
We then fix the reproduction number of symptomatic individuals and calculate fatalities at the population level as a function of the proportion of total non-symptomatic transmission and the proportion of non-symptomatic transmission that is caused by pre-symptomatic transmission.
Using the generalized non-symptomatic transmission model, we find a wide variety of scenarios for which peak fatalities occur at intermediate levels of non-symptomatic transmission in the presence of moderate to strong behavioral effects, $\delta > 0.6$ (Supplementary Figure S2).
One exception is the extreme (and unrealistic) case, in which all non-symptomatic transmission is caused by pre-symptomatic transmission;
in this case, total infections and fatalities are maximized when all transmission is caused by pre-symptomatic transmission. \jd{What?? If all transmission is pre-symptomatic, then we get no fatalities in our model.} \swp{what do you mean? if all non-symptomatic transmission is caused by pre-symptomatic transmission, then everyone eventually develops symptoms...}
Hereafter, we focus on asymptomatic infections for simplicity, but our conclusions have implications for the more general case of non-symptomatic transmission.
\jd{This is continuing to seem tangled to me. Should we reconsider the approach?}

>>>>

We therefore extend our model to consider the effects of generalized \textit{non-symptomatic} transmission, which includes both pre-symptomatic and asymptomatic transmission (Supplementary Figure S1), to ask the following question:
does an intermediate amount of non-symptomatic transmission lead to a peak in fatalities?
For this model, we assume that $\delta$ decreases transmission only after symptom onset.
We then fix the reproduction number of symptomatic individuals and calculate fatalities at the population level as a function of the proportion of total non-symptomatic transmission and the proportion of non-symptomatic transmission that is caused by pre-symptomatic transmission.
Using the generalized non-symptomatic transmission model, we find a wide variety of scenarios for which peak fatalities occur at intermediate levels of non-symptomatic transmission in the presence of moderate to strong behavioral effects, $\delta > 0.6$ (Supplementary Figure S2).
One exception is the extreme (and unrealistic) case, in which all non-symptomatic transmission is caused by pre-symptomatic transmission (i.e., there are no asymptomatic cases);
in this case, total infections and fatalities are maximized when all transmission is caused by pre-symptomatic transmission. 
Hereafter, we focus on asymptomatic infections for simplicity, but our conclusions have implications for the more general case of non-symptomatic transmission.
